---
title: "Class11: Structurtal Bioinformatics"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## The PDB database

The [PDB](http://www.rcsb.org/) is the main repository for biomolecular structure data.

Here we examine the contents of the PDB:

> Q1. Q1: Download a CSV file from the PDB site (accessible from “Analyze” > “PDB Statistics” > “by Experimental Method and Molecular Type”. Move this CSV file into your RStudio project and determine the percentage of structures solved by X-Ray and Electron Microscopy. From the website what proportion of structures are protein?

```{r}
db <- read.csv("Data Export Summary.csv", row.names=1)
head(db)
```

How many are X-Ray, etc...

```{r}
(db$Total/sum(db$Total)) * 100
```

What precent are Protein...

```{r}
(sum(db$Proteins)/sum(db$Total)) * 100
```

We could also try the datapasta package and copy from website and 
"Addins" > "Paste as data.frame"...

```{r}
library(datapasta)

tmp <- data.frame(stringsAsFactors=FALSE,
   Experimental.Method = c("X-Ray", "Other", "NMR", "Multi Method",
                           "Electron Microscopy", "Total"),
              Proteins = c(126880, 256, 11062, 129, 2277, 140604),
         Nucleic.Acids = c(2012, 4, 1279, 5, 31, 3331),
    ProteinComplex = c(6547, 6, 259, 2, 800, 7614),
                 Other = c(8, 13, 8, 1, 0, 30),
                 Total = c(135447, 279, 12608, 137, 3108, 151579)
)



```

 > Q2. Type HIV in the PDB website search box on the home page and determine how many HIV-1 protease structures are in the current PDB?
 
 
 There are 1157 as of 2019-05-07 See:
 http://www.rcsb.org/pdb/results/results.do?tabtoshow=Current&qrid=40D8F533
 
 
 ## Section 3 Usding Bio3D
 
```{r}
library(bio3d)

pdb <- read.pdb("1hsg.pdb")
pdb
```
 
 
```{r}
aa321(pdb$atom$resid)
```
 
Atom selection is done via the function **atom.select()**

```{r}
inds <- atom.select(pdb, "ligand")
```

```{r}
pdb$atom[inds$atom, ]
```
 
 

 
```{r}
prot.pdb <- atom.select(pdb, "protein", value=TRUE)
write.pdb(prot.pdb, file="1hsg_protein.pdb")
```
 

```{r}
lig.pdb <- atom.select(pdb, "ligand", value=TRUE)
write.pdb(lig.pdb, file="1hsg_ligand.pdb")
```
 

## SECTION 5

Adenylate kinase structure analysis from PDB

First get the sequence of Adenylate kinase from the 1AKE entry

```{r}
aa <- get.seq("1ake_A")
```

```{r}
aa
```

Now blast that against the entire PDB database

```{r}
# Blast or hmmer search
b <- blast.pdb(aa)

```

```{r}
# Plot a summary of search results
hits <- plot(b)
```


# Fix the section that needs simplifing

```{r}
# Load the package
library("bio3d.view")

```

```{r}
view.pdb(atom.select(pdb, "protein", value = TRUE), "overview", col="sse")
```

```{r}
view.pdb(atom.select(pdb, "ligand", value = TRUE), "overview", col="sse")
```


Or tiddyverse style...

```{r}
library(tidyverse)

pdb %>% atom.select(string="ligand", value=TRUE) %>% view.pdb()
```

```{r}
library(rgl)
view.pdb(pdb, "overview", col="sse")
rglwidget()
```


## Lets just try NMA

Here we will take a PDB structure from the database and perforem NMA

```{r}
p <- read.pdb("1hel")
modes <- nma(p)
```

```{r}
plot(modes)
```



```{r}
m7 <- mktrj(modes, mode=7, file="mode_7.pdb")
view.xyz(m7, col=vec2color(rmsf(m7)))

```

```{r}
view.nma <- function(modes, mode=7) { 
  m <- mktrj(modes, mode=mode)
  view.xyz(m, col=vec2color(rmsf(m)))
}
```

```{r}
view.nma(modes, 7)
```

```{r}
ids <- c("1TND_B","1AGR_A","1TAG_A","1GG2_A","1KJY_A","4G5Q_A")
files <- get.pdb(ids, split = TRUE)

```

```{r}
pdbs <- pdbaln(files, fit = TRUE)

```

```{r}
pc.xray <- pca(pdbs)

```

```{r}
plot(pc.xray)
```

```{r}
# Visualize first principal component
pc1 <- mktrj(pc.xray, pc=1, file="pc_1.pdb")

```

```{r}
view.xyz(pc1)
```

